
\documentclass[fleqn, letterpaper]{article}
\usepackage{amssymb,amsmath}
\usepackage[left=2.3cm,top=2.3cm,right=2.3cm,nohead,nofoot]{geometry}
\usepackage{verbatim}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{tabu}
\usepackage{url}

%\title{MA 105 Chapter 1 Project}

\begin{document}
%\maketitle
\noindent




\begin{center}\textbf{MA 105 Chapter 1 Project}\end{center}

\noindent
\begin{bf}MA 105-03 Maj. Givler

\noindent
Fall 2016\\
Due: 9 September 2016 in class
\end{bf}

\vspace{1 cm}
\noindent
{\bfseries Directions:} Read each section carefully. Please answer in complete sentences. You may brainstorm topic ideas with other cadets (section 1), but all other sections should be your own work. You may consult me for clarification, use your book and notes, and use the Writing Center for help. 

\vspace{.5 cm}
\noindent
{\bfseries 1.} Choose a topic that interests you or a question you would like to answer and describe it in a paragraph or two. Give relevant background information as needed.\\

\noindent
{\bfseries 2.} Describe how you could develop a statistical study to investigate your topic. Is your study experimental or observational? What data would you collect and how would you collect it? How would you categorize the data?\\

\noindent
{\bfseries 3.} Describe some common issues (2-3) for studies similar to your study and how your study would avoid them. Does your study have any potential lurking variables?\\

\noindent
{\bfseries 4.} Is your study feasible to conduct? If so, how could you extend your study? If it is not feasible, what additional resources would you need?\\


Your assignment should be formatted like a short research paper, however you do not need to include section headers. Your assignment should be typed and printed for class, but be sure to keep an electronic copy.

\end{document}

